Assessing the spatial patterning of Middle Paleolithic human settlement in Western Iberia

### 2020-10-22 analysis/paper/paper.Rmd
open-air-plot caption

```{r open-air-plots, eval = FALSE, echo = FALSE}

>>>>

```{r open-air-plots, eval = FALSE, echo = FALSE, fig.cap = "Kernel density plots comparing open-air sites and randomly resampled background points for A) Elevation, B) Slope, C) Aspect, and D) Distance to rivers. The grey areas represent the 95% confidence interval calculated from the resampling."}
